\chapter{Project Scope}
The CHSR project is a statewide infrastructure initiative aimed at establishing the nation's first high-speed rail system. Its primary goal is to design, construct, and operate an electrified rail line that can exceed speeds of 200 mph, connecting the San Francisco Bay Area and the Los Angeles Basin through the Central Valley. This initiative has two phases: Phase 1 is underway, and Phase 2 involves future extensions to Sacramento and San Diego \citep{ureport2023}.

\section{Deliverables}
The core deliverables include:
\begin{itemize}
	\item The rail infrastructure (track, tunnels, viaducts, and stations).
	\item Electrified rolling stock (high-speed trains with Tier III compliance).
	\item Communication and signaling systems.
	\item Maintenance facilities and operations control centers.
	\item Environmental mitigation and community integration measures.
\end{itemize}
The 2025 Project Update Report states that the authority “will connect the [CHSR]’s Early Operating Service (Merced to Bakersfield),” planned in 2022 \citep{plan2022}, “to the newly electrified Caltrain system via Gilroy, creating immediate regional benefits” \citep{ureport2025}. This segment aims to showcase the project’s feasibility, benefits, and safety before proceeding with further development.

\section{Requirements}
The project utilizes advanced electrically powered, steel-wheel-on-steel-rail technology, capable of reaching speeds of up to 220 mph on grade-separated segments \citep{purpose2022}. It aims to serve over 100 million annual riders upon completion. Modern safety, signaling, and automated train control systems, including Positive Train Control and Early Earthquake Warning, are required.

Regulatory compliance with federal and state environmental laws mandates Environmental Impact Reports/Statements (EIR/EIS) for all projects. Biennial Project Update Reports and Business Plans must be submitted to the California Legislature, outlining progress, funding, and risks. The system will operate on 100\% renewable energy.

\section{Constraints}
The project faces several critical constraints. These include:
\begin{itemize}
	\item Financial constraints: a limited and uncertain funding pipeline reliant on state bonds, federal grants, and cap-and-trade revenues.
	\item Geographical challenges: rugged terrain, including the Tehachapi and San Gabriel mountains, that requires tunneling.
	\item Legal constraints: ongoing litigation from landowners, environmental groups, and political stakeholders.
	\item Time constraints: pressure on the schedule due to funding deadlines and public expectations.
\end{itemize}

\section{Assumptions}
\begin{itemize}
	\item Ongoing political and public support through successive state administrations.
	\item Consistent access to federal and state funding sources.
	\item A forecasted increase in California’s population and demand for intra-state travel.
	\item The viability of addressing existing legal and technical challenges without significant scope reductions

\end{itemize}

\section{Work Breakdown Structure (WBS)}  \vspace*{1em}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}m{#1}} % Left-aligned and vertically centered
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}   % Centered and vertically centered
\begin{center}
	\begin{tabularx}{\textwidth}{|@{ \ }L{7.6cm} C{7.595cm}@{}|}
		\hline
		\textbf{1. Planning \& Design} & \vspace*{9pt}
		\begin{itemize}[leftmargin=*, nosep]
		  \item Route \& Site Selection
		  \item Environmental Approvals
		  \item Engineering \& Architectural Design
		\end{itemize} \vspace*{9pt} \\
		\hline
		\textbf{2. Infrastructure Construction} & \vspace*{9pt}
		\begin{itemize}[leftmargin=*, nosep]
		  \item Earthwork \& Foundations
		  \item Track \& Structures (Bridges, Tunnels)
		  \item Stations \& Facilities
		\end{itemize}\vspace*{9pt} \\
		\hline
		\textbf{3. Systems \& Rolling Stock} & \vspace*{9pt}
		\begin{itemize}[leftmargin=*, nosep]
		  \item Power \& Signaling Systems
		  \item Communications \& IT
		  \item Train Procurement
		\end{itemize}\vspace*{9pt} \\
		\hline
		\textbf{4. Project Management \& Support} & \vspace*{9pt}
		\begin{itemize}[leftmargin=*, nosep]
		  \item Project Oversight
		  \item Land Acquisition
		  \item Legal \& Compliance
		\end{itemize}\vspace*{9pt} \\
		\hline
		\textbf{5. Testing \& Commissioning} &\vspace*{9pt}
		\begin{itemize}[leftmargin=*, nosep]
		  \item System Integration Testing
		  \item Safety Certification
		  \item Operational Trial Runs
		\end{itemize}\vspace*{9pt} \\
		\hline
		\textbf{6. Operations \& Handover} &\vspace*{9pt}
		\begin{itemize}[leftmargin=*, nosep]
		  \item Staffing \& Training
		  \item Service Launch
		  \item Ongoing Maintenance Readiness
		\end{itemize} \vspace*{9pt}\\
		\hline
	\end{tabularx}

\end{center}  \par